Back to ``Normal'' for the Disintegrating Planet Candidate KIC 12557548 \MakeLowercase{b}

### 2018-10-13 ms.tex
minor typos fixed after reading aloud.

\section{Introduction}\label{sec:intro}
\citet{rappaport} first reported the discovery of a highly unusual system in the \kepler\ field, KIC 12557548.
Its light curve exhibits flux dips with a period of 0.653 days.
Surprisingly, the flux dips are neither symmetric in shape nor constant in amplitude, varying from $\sim$0\% to $\sim$1.2\%.
The amplitudes of the flux dips are highly stochastic and unpredictable from one event to the next 0.653 days later.
This is radially different from a transiting planet, where the planet absorbs the same amount of light from the star each orbit and does so symmetrically about the star, modulo stellar inhomogenities.
The time variability of the flux dips indicates that material with a projected area $\sim$1\% of the stellar surface is created and cleared in $\lesssim$ 1 day timescales in order to extinct $\sim$1\% of starlight at one epoch and $\sim$0\% at another.
These unusual light curve behaviors are best explained as dust extinction from a comet-like tail of material that is escaping a rocky planet (KIC 12557548 b, hereafter \sha) in a short period orbit.
The comet-like shape of the dust explains the asymmetric shape of the light curve profile.
The KIC 12557548/KOI-3794/Kepler-1520 system (hereafter \shStar) has the exciting possibility of being an opportunity to study a planet that has been peeled away layer by layer to reveal an interior core.

@@

Furthermore, there are perplexing systems that also display stochastic transit behavior but for which there are still no fully agreed-upon explanations: KIC 8462852 (ie. Boyajian's star) \citep{boyajian846}, RIK-210/EPIC 205483258 \citep{david2017rik210},  and PTFO 8-8695 \citep{vanEyken2012ptfTTauri}.
KIC 8462852 may be a family of comets from one or more parent bodies that recently broke apart \citep{boyajian846,bodman2016kic8462852cometFamily,wright2016familiesOfSolutions}.
\added{Similarly, a new system (KIC 3542116) has been discovered that has a light curve explained by extrasolar comets that produce transits in broadband optical light \citep{rappaport2018exocomets}.}
RIK-210 and PTFO 8-8695 are both in young systems ($\lesssim$ 10 and $\lesssim$3 Myr, respectively), so they may be proto-planet candidates or structures within a protoplanetary disk \citep{stauffer2017orbitingClouds,yu2015ptfO8d8695PlanetHypothesisTest}.
RIK-210 could be accreting material that causes variable extinction while PTFO 8-8695's orbit may be precessing and causing variations in transit depth depending on its longitude, though only portions of the lightcurve are explained this way \citep{barnes2013PTFO8d8695NodalPrecession,yu2015ptfO8d8695PlanetHypothesisTest}.

@@

\begin{figure}
\begin{centering}
\includegraphics[width=0.49\textwidth]{figure_index_152.pdf}
\includegraphics[width=0.49\textwidth]{stamps_kic1255_UT2016_07_14.pdf}
\caption{{\it Left:} \shStar\ (src) and reference stars (numbered) used on UT 2016-07-14 are shown over the full 9.8\arcmin $\times$ 9.8\arcmin\ Field of View of Mont4K.
{\it Right:} Postage stamp zoom-ins for the source and reference stars show the point spread functions for each star.
The reference stars were chosen to have similar count levels as \shStar.
}\label{fig:refStars}
\end{centering}
\end{figure}

@@

The first eigenvector largely corresponds to models of small dust grains with more isotropic scattering so that the light curve is dominated by extinction \citep{budaj12,brogi2012}.
We also note that the second eigenvector resembles models of large dust grains of pyroxene from \citet{budaj12}, where the particles that are a similar order of magnitude as the wavelength exhibit forward scattering, which causes a pronounced pre-ingress flux increase.
The second eigenvector has a broader forward scattering peak than the \citet{budaj12} models, so it may be the result of a broader distribution of particles.
The fact that the pre-ingress flux increase is not found in the first eigenvector and instead is pronounced in orthogonal eigenvectors suggests that the dust particle sizes may be changing in time.
We would expect that a dust tail with a variable number of of particles but a constant grain size would \deleted{be} exhibit a forward scattering in the first principal component because the forward scattering flux would scale proportionally with the number of particles and transit depth.
The implication of the PCA then is that the dust particle sizes may be changing with time.
\added{We assess the uncertainty of this conclusion through the time series of the principal components.}

@@

We suspect that sublimating asteroids around WD1145+017, the \sha\ and K2-22 b have long term behavior determined by surface features.
If alternating layers of rocky material have different composition, sublimation temperatures or albedos, they could provide a natural way to regulate the sublimation rate of the surface.
Alternatively, the chance alignment of starspots with the planet could regulate the planet disintegration \citep{kawahara2013starspots} and create periodic behaviors depending on the alignment of stellar rotation with the planet's position within its orbit.
\sha\ exhibits large stochastic variance that occasionally shuts off during quiescent intervals.
The transit activity level of WD1145+017's exhibits more complicated time dependence because there are many separate planetesimals or recently broken-up fragments that can serve as sources of dust \citep{vanderburg2015wdDisintegrating}.
}

@@

The host star \shStar\ has been characterized by both photometry and spectroscopy to better understand the system and parameters of the disintegrating planet and debris.
Table \ref{tab:stellObsParams} shows the summary of observations and analyses compiled in \citet{vanlieshout2016kic1255} for the stellar properties, re-produced here with additional results added from \citet{morton2016falsePos} and this work.
In the photometric analysis and low resolution spectroscopy, the spectra are consistent with a 4500 K main sequence K-type star.
High resolution spectra, however, indicated a higher temperature 4900 K lower log(g) sub-giant star \citep{kawahara2013starspots}.
\citet{vanlieshout2016kic1255} analyzed the light curve with a dust model to put constraints on the semi-major axis in terms of stellar radii, which can be combined with Kepler's third law to calculate the stellar density \citep{seager2003uniqueSolution}.
\citet{vanlieshout2016kic1255} find that the stellar density is only consistent with a main-sequence star with log(g) $\gtrsim 4.4 \log($cm s$^{-2})$.
\citet{vanlieshout2016kic1255} suggest an intriguing possibility that the high resolution spectrum of \shStar\ has contamination from dusty debris from the planet and thus appears as a sub-giant star.
If true, high resolution spectra would be valuable tool to study the composition and dynamics of the material escaping \sha.
In this section, we analyze archival high resolution spectra to put new constraints on the stellar temperature and surface gravity.

@@

After initial constraints on the models from the sensitivity to parameters search, we downloaded a grid of BOSZ models with effective temperatures ranging from 4250 K to 4750 K, Log(g) from 4.0 to 4.5, [M/H] from 0.0 to 0.5, [C/M]=0.0 and [$\alpha$/M] = -0.25 to 0.0.
We found the model with the  $\chi^2$ statistic over the Mg I triplet lines from 5160 to 5190 $\AA$
The minimum $\chi^2$ model for this entire grid is the same as shown in Figure \ref{fig:boszModelParamsMedianSpec} on the Bottom Right: T$_\mathrm{eff}$=4500 K, Log(g)=4.5, [M/H]=0.0, [C/M]=0.0, $\alpha=-0.25$.
This is similar to the log(g)$\approx$4.6, T$_\mathrm{eff}$=4500 stellar parameters derived from photometry and low resolution spectroscopy listed in Table \ref{tab:stellObsParams}.

@@

We also confirm our finding that the star is a main sequence using the Gaia DR2 parallax of 1.617 $\pm$ 0.030 mas \citep{gaia2016mission,gaia2018dr2,luri2018parallaxes}.
We follow the methodology from \citet{stassun2017gaiaRadiiMasses}, which is to estimate the bolometric flux from the spectral energy distribution and invert the Stefan-Boltman law to solve for the radius.
For the measured spectral energy distribution, we use the VizieR photometry service and fit this with a representative 4600 K \citet{castelli2004models} model and a (E-B)=0.05 diffuse Milky Way extinction model \citep{cardelli1989}.
We use the \texttt{pysynphot} tool \citep{lim2015pysynphot} to calculate the model and extinction.
We note that the exact stellar model used is less important than finding a function to fit the Spectral Energy Distribution.
When inverting the Stefan-Boltzman law, we assume an effective temperature of 4400 $\pm$ 70 K from our spectral fitting in Section \ref{sec:SpecMatch-Emp} and a photometric error of 5\%, assumed to be dominated by photometric systematics.
Using this method we find a radius of 0.72 $\pm$ 0.03 R$_\odot$, which is consistent with a main sequence star.
}

@@

High values of $f_S$ are possible for longitudinally symmetric distributions of active regions, such as a latitudinal band or polar spot.
Polar spots are indeed observed on rapidly rotating stars via Doppler imaging \citep{strassmeier2009starspots}; however, one would be unlikely on \sha, given its relatively long rotation period.
Additionally, the large physical size of \sha, as indicated by a transit duration longer than the time to cross the star, meaning that spots are likely to be crossed and thus diminish the transit source effect further.
In this light, \sha's $\sim$30\% observed transit depth variation at a $\sim$ 22 day period would require a pathological distribution of magnetically active regions to be explained by un-occulted spots.
If the spot distribution is polar or distributed in a latitudinal band, this would produce a bias at all epochs, unlike the time-dependent transit depth variations observed in \sha.
Therefore, the conclusion from \citet{croll2015starspots} that un-occulted spots are unlikely to cause the correlation between transit depth and stellar flux is likely correct even when considering a more realistic scaling relation between spot covering fraction and rotational modulation amplitude.
}

@@

\section{Acknowledgements}
%Thanks to Alessondra Springman for good resources on core and mantle compositions and the gases that could sublimate off of them.
%MCMC fitting makes use of \texttt{emcee} \citep{foreman-mackey2013emcee} and the covariance plot was made with \texttt{corner.py} \citep{foremanCorner}.
The authors thank to Kento Masuda for sharing the 2015 Subaru spectrum of \shStar\ and giving helpful comments on this work.
Funding for E Schlawin is provided by NASA Goddard Spaceflight Center.
\added{This work was supported by Japan Society for Promotion of Science (JSPS) KAKENHI Grant Number JP16K17660.
Support for this work was provided by NASA through Hubble Fellowship grant HST-HF2-51399.001 awarded by the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc., for NASA, under contract NAS5-26555.}
\replaced{The authors thank Benjamin Rackham for providing an estimate of the transit light source effect for a K4 V star and for helpful comments from Saul Rappaport.}{The authors thank Saul Rappaport for helpful comments.} % Now Ben is a coauthor
\added{This research has made use of the VizieR catalogue access tool, CDS, Strasbourg, France. The original description of the VizieR service was published in \citet{ochsenbein2000vizieR}.
This work has made use of data from the European Space Agency (ESA) mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed by the {\it Gaia} Data Processing and Analysis Consortium (DPAC,\url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}).
Funding for the DPAC has been provided by national institutions, in particular the institutions participating in the {\it Gaia} Multilateral Agreement.
This publication makes use of data products from the Wide-field Infrared Survey Explorer, which is a joint project of the University of California, Los Angeles, and the Jet Propulsion Laboratory/California Institute of Technology, funded by the National Aeronautics and Space Administration.}

>>>>

\section{Introduction}\label{sec:intro}
\citet{rappaport} first reported the discovery of a highly unusual system in the \kepler\ field, KIC 12557548.
Its light curve exhibits flux dips with a period of \replaced{0.653}{0.654} days.
Surprisingly, the flux dips are neither symmetric in shape nor constant in amplitude, varying from $\sim$0\% to $\sim$1.2\%.
The amplitudes of the flux dips are highly stochastic and unpredictable from one event to the next \replaced{0.653}{0.654} days later.
This is \replaced{radially}{radically} different from a transiting planet, where the planet absorbs the same amount of light from the star each orbit and does so symmetrically about the star, modulo stellar inhomogenities.
The time variability of the flux dips indicates that material with a projected area $\sim$1\% of the stellar surface is created and cleared in $\lesssim$ 1 day timescales in order to extinct $\sim$1\% of starlight at one epoch and $\sim$0\% at another.
These unusual light curve behaviors are best explained as dust extinction from a comet-like tail of material that is escaping a rocky planet (KIC 12557548 b, hereafter \sha) in a short period orbit.
The comet-like shape of the dust explains the asymmetric shape of the light curve profile.
The KIC 12557548/KOI-3794/Kepler-1520 system (hereafter \shStar) has the exciting possibility of being an opportunity to study a planet that has been peeled away layer by layer to reveal an interior core.

@@

Furthermore, there are perplexing systems that also display stochastic transit behavior but for which there are still no fully agreed-upon explanations: KIC 8462852 (ie. Boyajian's star) \citep{boyajian846}, RIK-210/EPIC 205483258 \citep{david2017rik210}  and PTFO 8-8695 \citep{vanEyken2012ptfTTauri}.
KIC 8462852 may be a family of comets from one or more parent bodies that recently broke apart \citep{boyajian846,bodman2016kic8462852cometFamily,wright2016familiesOfSolutions}.
\added{Similarly, a new system (KIC 3542116) has been discovered that has a light curve explained by extrasolar comets that produce transits in broadband optical light \citep{rappaport2018exocomets}.}
RIK-210 and PTFO 8-8695 are both in young systems ($\lesssim$ 10 and $\lesssim$3 Myr, respectively), so they may be proto-planet candidates or structures within a protoplanetary disk \citep{stauffer2017orbitingClouds,yu2015ptfO8d8695PlanetHypothesisTest}.
RIK-210 could be accreting material that causes variable extinction while PTFO 8-8695's orbit may be precessing and causing variations in transit depth depending on its longitude, though only portions of the lightcurve are explained this way \citep{barnes2013PTFO8d8695NodalPrecession,yu2015ptfO8d8695PlanetHypothesisTest}.

@@

\begin{figure}
\begin{centering}
\includegraphics[width=0.49\textwidth]{figure_index_152.pdf}
\includegraphics[width=0.49\textwidth]{stamps_kic1255_UT2016_07_14.pdf}
\caption{{\it Left:} \shStar\ (src) and reference stars (numbered) used on UT 2016-07-14 are shown over the full 9.8\arcmin $\times$ 9.8\arcmin\ Field of View of \added{the} Mont4K \added{imager}.
{\it Right:} Postage stamp zoom-ins for the source and reference stars show the point spread functions for each star.
The reference stars were chosen to have similar count levels as \shStar.
}\label{fig:refStars}
\end{centering}
\end{figure}

@@

The first eigenvector largely corresponds to models of small dust grains with more isotropic scattering so that the light curve is dominated by extinction \citep{budaj12,brogi2012}.
We also note that the second eigenvector resembles models of large dust grains of pyroxene from \citet{budaj12}, where the particles that are a similar order of magnitude as the wavelength exhibit forward scattering, which causes a pronounced pre-ingress flux increase.
The second eigenvector has a broader forward scattering peak than the \citet{budaj12} models, so it may be the result of a broader distribution of particles.
The fact that the pre-ingress flux increase is not found in the first eigenvector and instead is pronounced in orthogonal eigenvectors suggests that the dust particle sizes may be changing in time.
We would expect that a dust tail with a variable number of \deleted{of} particles but a constant grain size would \deleted{be} exhibit a forward scattering in the first principal component because the forward scattering flux would scale proportionally with the number of particles and transit depth.
The implication of the PCA then is that the dust particle sizes may be changing with time.
\added{We assess the uncertainty of this conclusion through the time series of the principal components.}

@@

We suspect that sublimating asteroids around WD1145+017, \sha\ and K2-22 b have long term behavior determined by surface features.
If alternating layers of rocky material have different composition, sublimation temperatures or albedos, they could provide a natural way to regulate the sublimation rate of the surface.
Alternatively, the chance alignment of starspots with the planet could regulate the planet disintegration \citep{kawahara2013starspots} and create periodic behaviors depending on the alignment of stellar rotation with the planet's position within its orbit.
\sha\ exhibits large stochastic variance that occasionally shuts off during quiescent intervals.
The transit activity level of WD1145+017's exhibits more complicated time dependence because there are many separate planetesimals or recently broken-up fragments that can serve as sources of dust \citep{vanderburg2015wdDisintegrating}.
}

@@

The host star \shStar\ has been characterized by both photometry and spectroscopy to better understand the system and parameters of the disintegrating planet and debris.
Table \ref{tab:stellObsParams} shows the summary of observations and analyses compiled in \citet{vanlieshout2016kic1255} for the stellar properties, re-produced here with additional results added from \citet{morton2016falsePos} and this work.
In the photometric analysis and low resolution spectroscopy, the spectra are consistent with a 4500 K main sequence K-type star.
High resolution spectra, however, indicated a higher temperature 4900 K lower log(g) sub-giant star \citep{kawahara2013starspots}.
\citet{vanlieshout2016kic1255} analyzed the light curve with a dust model to put constraints on the semi-major axis in terms of stellar radii, which can be combined with Kepler's third law to calculate the stellar density \citep{seager2003uniqueSolution}.
\citet{vanlieshout2016kic1255} find that the stellar density is only consistent with a main-sequence star with log(g) $\gtrsim 4.4 \log($cm s$^{-2})$.
\citet{vanlieshout2016kic1255} suggest an intriguing possibility that the high resolution spectrum of \shStar\ has contamination from dusty debris from the planet and thus appears as a sub-giant star.
If true, high resolution spectra would be \added{a} valuable tool to study the composition and dynamics of the material escaping \sha.
In this section, we analyze archival high resolution spectra to put new constraints on the stellar temperature and surface gravity.

@@

After initial constraints on the models from the sensitivity to parameters search, we downloaded a grid of BOSZ models with effective temperatures ranging from 4250 K to 4750 K, Log(g) from 4.0 to 4.5, [M/H] from 0.0 to 0.5, [C/M]=0.0 and [$\alpha$/M] = -0.25 to 0.0.
We found the model with the  $\chi^2$ statistic over the Mg I triplet lines from 5160 to 5190 $\AA$.
The minimum $\chi^2$ model for this entire grid is the same as shown in Figure \ref{fig:boszModelParamsMedianSpec} on the Bottom Right: T$_\mathrm{eff}$=4500 K, Log(g)=4.5, [M/H]=0.0, [C/M]=0.0, $\alpha=-0.25$.
This is similar to the log(g)$\approx$4.6, T$_\mathrm{eff}$=4500 stellar parameters derived from photometry and low resolution spectroscopy listed in Table \ref{tab:stellObsParams}.

@@

We also confirm our finding that the star is a main sequence using the Gaia DR2 parallax of 1.617 $\pm$ 0.030 mas \citep{gaia2016mission,gaia2018dr2,luri2018parallaxes}.
We follow the methodology from \citet{stassun2017gaiaRadiiMasses}, which is to estimate the bolometric flux from the spectral energy distribution and invert the Stefan-Boltman law to solve for the radius.
For the measured spectral energy distribution, we use the VizieR photometry service and fit this with a representative 4600 K \citet{castelli2004models} model and a (E-B)=0.05 diffuse Milky Way extinction model \citep{cardelli1989}.
We use the \texttt{pysynphot} tool \citep{lim2015pysynphot} to calculate the model and extinction.
We note that the exact stellar model used is less important than finding a function to fit the Spectral Energy Distribution.
When inverting the Stefan-Boltzman law, we assume an effective temperature of 4440 $\pm$ 70 K from our spectral fitting in Section \ref{sec:SpecMatch-Emp} and a photometric error of 5\%, assumed to be dominated by photometric systematics.
Using this method we find a radius of 0.72 $\pm$ 0.03 R$_\odot$, which is consistent with a main sequence star.
}

@@

High values of $f_S$ are possible for longitudinally symmetric distributions of active regions, such as a latitudinal band or polar spot.
Polar spots are indeed observed on rapidly rotating stars via Doppler imaging \citep{strassmeier2009starspots}; however, one would be unlikely on \sha, given its relatively long rotation period.
Additionally, the large physical size of \sha's tail, as indicated by a transit duration longer than the time to cross the star, means that spots are likely to be crossed and this diminishes the transit source effect further.
In this light, \sha's $\sim$30\% observed transit depth variation at a $\sim$ 22 day period would require a pathological distribution of magnetically active regions to be explained by un-occulted spots.
If the spot distribution is polar or distributed in a latitudinal band, this would produce a bias at all epochs, unlike the time-dependent transit depth variations observed in \sha.
Therefore, the conclusion from \citet{croll2015starspots} that un-occulted spots are unlikely to cause the correlation between transit depth and stellar flux is likely correct even when considering a more realistic scaling relation between spot covering fraction and rotational modulation amplitude.
}

@@

\section{Acknowledgements}
%Thanks to Alessondra Springman for good resources on core and mantle compositions and the gases that could sublimate off of them.
%MCMC fitting makes use of \texttt{emcee} \citep{foreman-mackey2013emcee} and the covariance plot was made with \texttt{corner.py} \citep{foremanCorner}.
The authors thank to Kento Masuda for sharing the 2015 Subaru spectrum of \shStar\ and giving helpful comments on this work.
Funding for E Schlawin is provided by NASA Goddard Spaceflight Center.
\replaced{The authors thank Benjamin Rackham for providing an estimate of the transit light source effect for a K4 V star and for helpful comments from Saul Rappaport.}{The authors thank Saul Rappaport for helpful comments.} % Now Ben is a coauthor
\added{Thanks to Ben Weiner for some useful discussion on high resolution spectroscopy.
This work was supported by the Japan Society for Promotion of Science (JSPS) KAKENHI Grant Number JP16K17660.
Support for this work was provided by NASA through Hubble Fellowship grant HST-HF2-51399.001 awarded by the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc., for NASA, under contract NAS5-26555.}
\added{This research has made use of the VizieR catalogue access tool, CDS, Strasbourg, France. The original description of the VizieR service was published in \citet{ochsenbein2000vizieR}.
This work has made use of data from the European Space Agency (ESA) mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed by the {\it Gaia} Data Processing and Analysis Consortium (DPAC,\url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}).
Funding for the DPAC has been provided by national institutions, in particular the institutions participating in the {\it Gaia} Multilateral Agreement.
This publication makes use of data products from the Wide-field Infrared Survey Explorer, which is a joint project of the University of California, Los Angeles, and the Jet Propulsion Laboratory/California Institute of Technology, funded by the National Aeronautics and Space Administration.}
